Type Visualization for R

### 2020-06-17 paper/main.tex
paper: Add images

@@

@@

>>>>

We interviewed the primary researcher developing R's gradual type system
to inventory relevant domain-specific tasks.
Additionally, we sought feedback throughout the creation of {\sc TypeVis}
to ensure it was adequately satisfying requirements.
The domain-specific goals can be reduced to:

\begin{enumerate}
\item {\bf Find Function.} Quickly search for a particular function and identify basic information. This includes how often the function is called and which package contains it.
\item {\bf Determine Types.} Given a specific function, determine the argument and return types of the function. Additionally, identify the frequency of a type signature. A user should be able to infer, for example, if the function is polymorphic or if it's a predicate.
\item {\bf Compare Signatures.} Compare the occurrence of type signatures within a specific function, but also across many different ones. Users must be able to isolate individual signatures and see them in the context of other signatures and functions.
\end{enumerate}

These goals can be classified using an abstract task analysis framework.
In table~\ref{tab:tasks}, we use Munzner's mid-level and low-level
abstract task taxonomy. \todo{Cite Munzner}

@@

\begin{figure*}
 \centering
 \includegraphics[width=\linewidth]{img/typevis.png}
 \caption{The main view of {\sc TypeVis}, with type flows on the left and the package hierarchy on the right.}
 \label{fig:typevis}
\end{figure*}

\begin{figure}[tb]
 \centering
 \includegraphics[width=\columnwidth]{img/no_decross.png}
 \includegraphics[width=\columnwidth]{img/decross.png}
 \caption{Comparison of type flows without decrossing (above) and with decrossing (below).}
 \label{fig:decross}
\end{figure}

@@

\subsection{Package and Function Filtering}

\subsection{Types as Flows}

\subsection{Technical Details}
